---
title: "MVLS LTS Network Outputs"
last-updated: "Auto-updated weekly"
---

```{r}
#| label: setup
#| include: false

library(jsonlite)
library(dplyr)
library(tidyr)
library(glue)

# Load publication data
pub_data <- fromJSON(here::here("_data", "publications.json"))
```

## Overview

This website provides an automatically updated list of outputs from the College of MVLS Learning Teaching and Scholarship network at the University of Glasgow. Publication data is sourced directly from [ORCID](https://orcid.org) profiles and updated weekly via GitHub Actions.

If you are a member of staff and would like your ORCID to be added, please complete the spreadsheet located in the Scholarship section of the [MVLS LTS Network Sharepoint](https://gla.sharepoint.com/sites/CollegeMVLS-LearningTeaching/SitePages/MVLS-LTS-Network.aspx).

::: callout-note
## Current Statistics

-   **`r pub_data$n_authors`** linked authors
-   **`r pub_data$n_sotl`** SoTL/education outputs
-   **Last updated:** `r pub_data$last_updated`
:::

## Recent SoTL Publications

Publications are automatically classified based on journal name and keywords to identify those related to the **Scholarship of Teaching and Learning (SoTL)** and those that are likely to be discipline-specific, so errors may occur. 

```{r}
#| label: recent-pubs
#| echo: false
#| results: asis

pubs <- pub_data$publications |>
 as_tibble() |>
 filter(type == "journal-article",
        !is.na(sotl_matched_on)) |>
 head(10)

for (i in seq_len(nrow(pubs))) {
  pub <- pubs[i, ]
  
  # Build citation string with school in brackets
  author_text <- if (!is.na(pub$network_authors_school) && pub$network_authors_school != "") {
    glue("{pub$network_authors_school}. ")
  } else {
    ""
  }
  
  title_text <- if (!is.na(pub$url) && pub$url != "") {
    glue("[{pub$title}]({pub$url})")
  } else {
    pub$title
  }
  
  year_text <- if (!is.na(pub$year)) glue(" ({pub$year})") else ""
  journal_text <- if (!is.na(pub$journal) && pub$journal != "") glue(" *{pub$journal}*.") else ""
  
  cat(glue("- {author_text}{title_text}{year_text}.{journal_text}\n\n"))
}
```

[View all publications →](publications.qmd)

## Quick Links

-   [Browse all outputs](publications.qmd) - Full searchable list
-   [Network authors](authors.qmd) - View all contributing authors
-   [About this site](about.qmd) - How this works
